---
title: "Data Science - Week 1"
author: "Kim Heagy"
format: html
editor: visual
---

## Questions

### What is a data scientist?

A data scientist is someone who collects, analyzes, and communicates data. They transform data into meaningful insights. This is an interdisciplinary role, so a data scientist may pull from several fields including computer science, math, engineering, and statistics. A data scientist can be an ambiguous term as it means a lot of different things to different people.

### Compare and contrast data scientists and statisticians

A statistician has more of a defined mathematical role which focuses on numeric, structured data sets. The statistician will focus on building models and stay within the world of science or math.Conversely, a data scientist can be more of a cross-functional role and may work with nontraditional data types. A data scientists have to critically think about how to use and process data to answer business or social questions.

### How do I fit into this?

I fit into this because I want to represent and communicate data accurately and clearly as a horticultural researcher. This means I need to have a background in statistics to handle data correctly. It also means I have to make decisions in how and which data to collect - this can take a long time to understand! Later I will make decision on how to analyze and then communicate this data to growers and other teammates in my lab or department. Here are some ways I hope to apply what I will learn in this class.

1.  Presenting grape virus poster at ASHS conference in September
2.  Compare and contrast strawberry yield data for cultivar evaluations
3.  Correlate consumer taste preferences with sugar levels in strawberries

```{r}
y <- density(iris$Sepal.Length)
```

### Data Set Information

Here is the class, type, and structure of the data set y.

```{r}
class(y)
typeof(y)
str(y)

```

### Plot of Sepel Length

Here is a plot of the Sepal Length vs. Density

```{r}
#| echo: false
plot(y)
```
